A survey of HTTP caching options on the open Web

### 2015-01-14 sanity/paper1.tex
Smaller proofreading
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@981 43ef1190-90fd-4dd7-a769-d0121f02b80e

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL Endpoints, ontologies, or other information resources,
by a spider detailed in Appendix~\ref{app:fetcher}, resulting in 7745
requests.

@@

\section{Analytics}

@@

We next consider the simple heuristic freshness lifetime. This is
implemented as suggested in RFC7234, Section~4.2.2. This is based on a
fraction of the time lapsed between the current time and the
modification time given in the \httph{Last-Modified} header. This
approach therefore still requires the Web server to be cooperative to
be successful, but commonly, Web servers can track this, based e.g. on
the file modification time of the underlying file system.

@@

To allow generation and validation of \httph{Last-Modified} and
\httph{ETag} headers, DBMS authors should make sure it is much cheaper
to retrieve the modification time of any subgraph, than to retrieve
the subgraph itself. This would be a great improvement for
RFC7232-based caching, when revalidation is required. It would also
help simple heuristic based caching. Research in that direction has
been published in \cite{kaseicache}.

>>>>

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL Endpoints, ontologies, or other information resources,
by a spider detailed in Appendix~\ref{app:fetcher}, resulting in 7745
requests, done on 2015-01-02.

@@

\section{Analysis}

@@

We next consider the simple heuristic freshness lifetime. This is
implemented as suggested in RFC7234, Section~4.2.2. This is based on a
fraction of the time lapsed between the current time and the
modification time given in the \httph{Last-Modified} header. This
approach therefore still requires the Web server to be cooperative to
be successful, but commonly, Web servers can track this, for example
if RDF is served from a file system, the file modification time is used.

@@

To allow generation and validation of \httph{Last-Modified} and
\httph{ETag} headers, DBMS authors should make sure it is much cheaper
to retrieve the modification time of any subgraph, than to retrieve
the subgraph itself. This would be a great improvement for
RFC7232-based caching, when revalidation is required. It would also
help simple heuristics based caching. Research in that direction has
been published in \cite{kaseicache}.
